Apparent preferences for cognitive effort fade when multiple forms of effort and delay are interleaved in a foraging environment

### 2020-08-11 Cost_manuscript.Rmd
modeling note
things to address in the discussion

**new** The adaptive nature of choices in this experiment demanded more flexibility than the single-parameter model fitted above. Based on the results, an adequate model of behavior should meet X criteria: 1) an initial preference for cognitive effort trials 2) that this preference disappeared as acceptances devolved to a common rate across costs; 3) show that participants kept track of recent offer history; 4) that these effects were robust to block order effects; 5) deviations from optimality that were not simply due to overharvesting; and 6) be applicable to both experiments. Alternative foraging models from the literature were not fitted, as they did not qualitatively meet these criteria (wikenheiser, C&D, Fawcett...)

@@

- Working memory could produce timing issues (Buhi n Gershman). Efficiency couldn't be it because then global decrease wouldn't happen and phys effort might be affected too (Shenhav stuff). 
- Deviations in the willingness to pursue effort can predict depression relapse (https://jamanetwork.com/journals/jamapsychiatry/article-abstract/2761562), and motivational factors affecting effor aversion can be heterogenous between depression and schizophrenia (https://www.researchgate.net/publication/337361164_Pathways_to_Motivational_Impairments_in_Psychopathology_Common_Versus_Unique_Elements_Across_Domains). Like, the aversion is due to focusing on different elements of the task.
- Talk about future experiments: if this is subjective time, changing the pacing of the tasks should change the acceptance rates for cognitive effort
- It's true that we didnt calibrate cog effort per subject. But instead we brought all subjects to the same level of performance, and we saw that as time progressed they became less likely to accept longer periods of effort.

>>>>

**new** The adaptive nature of choices in this experiment demanded more flexibility than the single-parameter model fitted above. Based on the results across experiments, an adequate model of behavior should meet X criteria: 1) show deviations from optimality that were not simply due to overharvesting 2) persistently higher acceptances for cognitive effort when faced with single behavioral costs; 3) slight reduction of acceptances in effortful conditions (**fatigue?**); 4) an initial preference for cognitive effort trials when foraging for costs and rewards 5) this preference disappears as acceptances decreased to a common rate across costs; 6) participants kept track of recent offer history; 7) effects were robust to block order effects. Alternative foraging models from the literature were not fitted, as they did not qualitatively meet these criteria (wikenheiser, C&D, Fawcett...)

DIFFICULT TO MODEL: ALL COST ACCEPTANCES DECREASE AT LEAST A BIT. LEARNING SUBJECTIVE TIME DOESN'T DO THAT. IN FACT, IT STILL SEEMS AS IF THE EFFORT FATIGUE SEEN ON EXP 1 HAPPENS AGAIN, AND ALL COSTS DEFAULT TO THE COSTLIEST. THAT DOESN'T INVOLVE TIME NECESSARILY.

@@

- What we think: subjective timing is shortened by the way we implemented cognitive effort. This can be recalibrated if many task types are experienced. Maybe the implementation allowed for counting. Alternatively, working memory engagement could produce timing issues (Buhi n Gershman). Also look at what Andrew Westbrook shared.
- Things that don't seem to be at play here, but could still play a general role in mental effort preferences: 1) A demand’s cost is not fully intrinsic (within vs between differences); 2) Effort preferences unlikely just due to learned industriousness or efficacy as amitais lab sees it (differences between effort types, and everyone met a good performance level per training); 3) avoiding boredom (global decline in exp 2, not a preference exchange). 4) Literally counting tasks, since mental effort was discretely presented but everything else was contiguous. If that were the case, dividing the handling time by 2 would work, but not sure if it would translated into exp 2.
- Deviations in the willingness to pursue effort can predict depression relapse (https://jamanetwork.com/journals/jamapsychiatry/article-abstract/2761562), and motivational factors affecting effor aversion can be heterogenous between depression and schizophrenia (https://www.researchgate.net/publication/337361164_Pathways_to_Motivational_Impairments_in_Psychopathology_Common_Versus_Unique_Elements_Across_Domains). Like, the aversion is due to focusing on different elements of the task.
- Talk about future experiments: if this is subjective time, changing the pacing of the tasks should change the acceptance rates for cognitive effort
- It's true that we didnt calibrate cog effort per subject. But instead we brought all subjects to the same level of performance, and we saw that as time progressed they became less likely to accept longer periods of effort.
